\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Uitbreiding Attacks, Tables omgedraaid.

\begin{tabular}{|l|r|}
\hline
2206 & root \\ \hline
39 & admin \\ \hline
26 & bin \\ \hline
20 & w000t \\ \hline
19 & oracle \\ \hline
19 & jenny \\ \hline
\end{tabular}

@@

\begin{tabular}{|l|r|}
\hline
55 &  \\ \hline
28 & 123456 \\ \hline
20 & 111111 \\ \hline
16 & root \\ \hline
16 & admin \\ \hline
\end{tabular}

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Connection} we can conclude that our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.

Our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.

>>>>

\begin{tabular}{|l|r|}
\hline
Username & Attempts \\ \hline
root & 2206 \\ \hline
admin & 39 \\ \hline
bin & 26 \\ \hline
w000t & 20 \\ \hline
oracle & 19 \\ \hline
jenny & 19 \\ \hline
\end{tabular}

@@

\begin{tabular}{|l|r|}
\hline
Password & Attempts \\ \hline
  & 55 \\ \hline
123456 & 28 \\ \hline
111111 & 20 \\ \hline
root & 16 \\ \hline
admin & 16 \\ \hline
\end{tabular}

@@

\section{Conclusion}
\label{Conclusion}
From Section \ref{Attacks} we can conclude that our honeypot was not as popular as we had hoped it would be. Because we chose not to advertise, we solely relied on the hackers abilities to find us by for example portscans. The number of attacks on us was therefore not high and neither was the depth of the attacks.
